%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Mobileum India Pvt. Ltd.} % Organization
    {Bengaluru, India} % Location
    {Dec. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a Full Stack developer with DevOps expertise in the Security Firewall team.}
        \item {Contributed to the development of frontend UI for Security Firewall products that allowed users to manage and monitor their network security.}
        \item {Contributed to the development of GraphQL APIs for our firewall products, enabling efficient and flexible data access and manipulation.}
        \item {Contributed to the containerization of firewall products using Docker, which included writing Dockerfiles and Docker Compose files}
        \item {Leveraged Kubernetes for orchestration, creating Helm charts for package management and ensuring seamless application updates and rollbacks.}
        \item {Deployed containerized applications on AWS EKS, which included setting up EKS cluster, configuring and managing Kubernetes deployments.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Programmer Analyst Trainee} % Job title
    {Cognizant} % Organization
    {Kolkata, India} % Location
    {Sept. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a DevOps engineer mostly creating automation scripts and CI/CD pipelines.}
        \item {Worked with webhooks and CRON jobs in automation server Jenkins.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
